---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
library(regress431)
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

This was the product of a series of assignments in STAT 431 Advanced Programming in R at Cal Poly SLO, focused on building different regression methods from scratch in R.

##Demonstration of Regression Methods

#Ridge Regression
```{r}
my_result <- mtcars %>%
  dplyr::select(mpg, hp, cyl) %>%
  ridge_regression(mpg, lambda = 0.5)

mtcars2 <- mtcars %>%
  dplyr::select(mpg, cyl, hp) %>%
  dplyr::mutate(
    cyl = scale(cyl),
    hp = scale(hp)
    )

mass_result <- MASS::lm.ridge(mpg ~ hp + cyl, data = mtcars2, lambda = .5*32/31)

print(mass_result)
print(my_result)

```

#Selecting best lambda out of list for ridge regression
```{r}
lambdas <- 0:10*.1

my_result <- mtcars %>%
  dplyr::select(mpg, hp, cyl) %>%
  ridge_regression(mpg, lambda = lambdas)

print(my_result)

```

#Simple Linear Regression via Gradient Descent
```{r}
my_result <- mtcars %>%
  slr_gd(mpg, hp, errplot = T)

mass_result <- lm(mpg ~ hp, data = mtcars)

print(mass_result)
print(my_result)
```

#Multiple Linear Regression via Gradient Descent
```{r}
my_result <- mtcars %>%
  dplyr::select(mpg, hp, cyl) %>%
  mlr_gd(mpg)

mass_result <- lm(mpg ~ hp + cyl, data = mtcars)

print(mass_result)
print(my_result)
```

#Multiple Linear Regression via QR Decomposition
```{r}

my_result <- mtcars %>%
  dplyr::select(mpg, hp, cyl) %>%
  mlr_qr(mpg)

mass_result <- lm(mpg ~ hp + cyl, data = mtcars)

print(mass_result)
print(my_result)

```
